\documentclass[10pt,a4paper,twoside]{article}
\usepackage[dutch]{babel}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{float,flafter}	
\usepackage{hyperref}
\usepackage{inputenc}
\setlength\paperwidth{20.999cm}\setlength\paperheight{31.699cm}\setlength\voffset{-1in}\setlength\hoffset{-1in}\setlength\topmargin{.1cm}\setlength\headheight{12pt}\setlength\headsep{0cm}\setlength\footskip{1.131cm}\setlength\textheight{29cm}\setlength\oddsidemargin{2.499cm}\setlength\textwidth{15.999cm}

\begin{document}
\begin{center}
\hrule

\vspace{.4cm}
{\bf {\Large ASSIGNMENT-4 }}\\
\vspace{.3cm}
{\bf {\huge }}
\vspace{.3cm}
\end{center}
{\bf Name:}  BINAY KUMAR SETHI\\
{\bf Roll no:}  19111021 \\
{\bf Branch: }  Biomedical Engineering \hspace{\fill}  22 July, 2021 \\
\hrule

\vspace{.3cm}
{\bf Can AI be used to understand facts about the topic and bring that topics from pseudoscience to science}
\\
\\
Graphology is that the analysis of the physical characteristics and patterns of handwriting with plan to identify the author , indicate the mental state at the time of writing, or evaluate personality characteristics. No scientific evidence exists to support graphology, and it's generally considered a pseudoscience or scientifically questionably practice. However, it remains in widespread use in France and has historically been considered legitimate to be used in some lawsuits . The term is usually incorrectly wont to ask forensic document examination, thanks to the very fact that aspects of the latter handling the examination of handwritten documents are occasionally mentioned as graph analysis. \\
\\
\\
Artificial Intelligence (AI) advancements so far , which include machine learning tools and everything from Roombas cleaning pet hair and other smart technologies controlling your home, make life easier in some ways . Forensic handwriting analysis, for instance , is one discipline that's gaining prominence.Individual handwriting significantly differs from other people’s handwritings though there could also be some striking similarities. The difference in handwritings is visible in several signatures. It is pretty challenging to imitate another person’s name since this is often more of a private identification code. However, with continual practice, one can imitate another individual’s writing, and this poses different risks. Identical handwriting can cause cases of fraud , forgery, and fraud. As a result, victims can lose money in banks or other relevant personal information. Forensic handwriting analysis through the utilization of AI and machine learning can help in guarding against cases of fraud. For instance, handwriting recognition software can play a pivotal role in preventing data theft, but it also can have negative implications. this text , therefore, gives you insight about how machine learning tools can revolutionize forensic handwriting analysis. The combination of using these AI tools and a graphologist gives you the simplest answer.\\
\\
\\
Artificial intelligence tries to duplicate human handwriting through the utilization of software that analyses a bit of handwriting. The software then copies the handwriting when writing new sentences. University College London Computer Scientists developed the software. My Text In Your Handwriting may be a program that uses explicitly a machine learning algorithm that has glyphs. The glyphs are unique and specific ways upon which individuals shape different characters. The software learns things that are consistent across the literary genre then reproduce them after analyzing a neighborhood of writing. It also identifies other stuff like spacing in tour handwriting also as other irregularities.










\end{document}
